Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-27 graph_auto_exp1_distr_1_3.tex
Modify based on Mykel's feedback

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (15.2500,68.0000,0.0000) (15.2500,70.5000,0.0000) (9.0000,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.0000) (15.2500,70.5000,0.0000) (15.2500,93.5000,0.0000) (9.0000,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.0000) (15.2500,93.5000,0.0000) (15.2500,109.0000,0.0000) (9.0000,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.0020) (15.2500,109.0000,0.0020) (15.2500,159.5000,0.0020) (9.0000,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0235) (15.2500,159.5000,0.0235) (15.2500,259.0000,0.0235) (9.0000,259.0000,0.0235)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0030) (15.2500,259.0000,0.0030) (15.2500,284.5000,0.0030) (9.0000,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.1345) (15.2500,284.5000,0.1345) (15.2500,455.0000,0.1345) (9.0000,455.0000,0.1345)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.0000) (17.6500,68.0000,0.0000) (17.6500,70.5000,0.0000) (15.2500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.0000) (17.6500,70.5000,0.0000) (17.6500,93.5000,0.0000) (15.2500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.0000) (17.6500,93.5000,0.0000) (17.6500,109.0000,0.0000) (15.2500,109.0000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.0020) (17.6500,109.0000,0.0020) (17.6500,159.5000,0.0020) (15.2500,159.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.0230) (17.6500,159.5000,0.0230) (17.6500,259.0000,0.0230) (15.2500,259.0000,0.0230)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.0030) (17.6500,259.0000,0.0030) (17.6500,284.5000,0.0030) (15.2500,284.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.0625) (17.6500,284.5000,0.0625) (17.6500,455.0000,0.0625) (15.2500,455.0000,0.0625)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.0000) (20.9000,68.0000,0.0000) (20.9000,70.5000,0.0000) (17.6500,70.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.0000) (20.9000,70.5000,0.0000) (20.9000,93.5000,0.0000) (17.6500,93.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.0070) (20.9000,93.5000,0.0070) (20.9000,109.0000,0.0070) (17.6500,109.0000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.0430) (20.9000,109.0000,0.0430) (20.9000,159.5000,0.0430) (17.6500,159.5000,0.0430)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.0880) (20.9000,159.5000,0.0880) (20.9000,259.0000,0.0880) (17.6500,259.0000,0.0880)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.0095) (20.9000,259.0000,0.0095) (20.9000,284.5000,0.0095) (17.6500,284.5000,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.0225) (20.9000,284.5000,0.0225) (20.9000,455.0000,0.0225) (17.6500,455.0000,0.0225)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.0015) (25.6500,68.0000,0.0015) (25.6500,70.5000,0.0015) (20.9000,70.5000,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.0060) (25.6500,70.5000,0.0060) (25.6500,93.5000,0.0060) (20.9000,93.5000,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.0320) (25.6500,93.5000,0.0320) (25.6500,109.0000,0.0320) (20.9000,109.0000,0.0320)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.0945) (25.6500,109.0000,0.0945) (25.6500,159.5000,0.0945) (20.9000,159.5000,0.0945)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.0455) (25.6500,159.5000,0.0455) (25.6500,259.0000,0.0455) (20.9000,259.0000,0.0455)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.0000) (25.6500,259.0000,0.0000) (25.6500,284.5000,0.0000) (20.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.0070) (25.6500,284.5000,0.0070) (25.6500,455.0000,0.0070) (20.9000,455.0000,0.0070)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.0055) (28.9000,68.0000,0.0055) (28.9000,70.5000,0.0055) (25.6500,70.5000,0.0055)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.0110) (28.9000,70.5000,0.0110) (28.9000,93.5000,0.0110) (25.6500,93.5000,0.0110)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.0375) (28.9000,93.5000,0.0375) (28.9000,109.0000,0.0375) (25.6500,109.0000,0.0375)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.0545) (28.9000,109.0000,0.0545) (28.9000,159.5000,0.0545) (25.6500,159.5000,0.0545)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.0165) (28.9000,159.5000,0.0165) (28.9000,259.0000,0.0165) (25.6500,259.0000,0.0165)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.0000) (28.9000,259.0000,0.0000) (28.9000,284.5000,0.0000) (25.6500,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.0035) (28.9000,284.5000,0.0035) (28.9000,455.0000,0.0035) (25.6500,455.0000,0.0035)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.0030) (46.6000,68.0000,0.0030) (46.6000,70.5000,0.0030) (28.9000,70.5000,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.0995) (46.6000,70.5000,0.0995) (46.6000,93.5000,0.0995) (28.9000,93.5000,0.0995)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.0860) (46.6000,93.5000,0.0860) (46.6000,109.0000,0.0860) (28.9000,109.0000,0.0860)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.0605) (46.6000,109.0000,0.0605) (46.6000,159.5000,0.0605) (28.9000,159.5000,0.0605)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.0120) (46.6000,159.5000,0.0120) (46.6000,259.0000,0.0120) (28.9000,259.0000,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,284.5000,0.0000) (28.9000,284.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.0005) (46.6000,284.5000,0.0005) (46.6000,455.0000,0.0005) (28.9000,455.0000,0.0005)};

			\addplot3[mark=+, draw=none, mark size=1.0] coordinates {

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.24,...,1.3},
			        ylabel={probability density $\times 10^3$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.000000) (15.2500,68.0000,0.000000) (15.2500,70.5000,0.000000) (9.0000,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,70.5000,0.000000) (15.2500,70.5000,0.000000) (15.2500,93.5000,0.000000) (9.0000,93.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,93.5000,0.000000) (15.2500,93.5000,0.000000) (15.2500,109.0000,0.000000) (9.0000,109.0000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,109.0000,0.004752) (15.2500,109.0000,0.004752) (15.2500,159.5000,0.004752) (9.0000,159.5000,0.004752)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.031357) (15.2500,159.5000,0.031357) (15.2500,259.0000,0.031357) (9.0000,259.0000,0.031357)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.031373) (15.2500,259.0000,0.031373) (15.2500,284.5000,0.031373) (9.0000,284.5000,0.031373)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,284.5000,0.142639) (15.2500,284.5000,0.142639) (15.2500,455.0000,0.142639) (9.0000,455.0000,0.142639)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,68.0000,0.000000) (17.6500,68.0000,0.000000) (17.6500,70.5000,0.000000) (15.2500,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,70.5000,0.000000) (17.6500,70.5000,0.000000) (17.6500,93.5000,0.000000) (15.2500,93.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,93.5000,0.000000) (17.6500,93.5000,0.000000) (17.6500,109.0000,0.000000) (15.2500,109.0000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,109.0000,0.028878) (17.6500,109.0000,0.028878) (17.6500,159.5000,0.028878) (15.2500,159.5000,0.028878)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,159.5000,0.092127) (17.6500,159.5000,0.092127) (17.6500,259.0000,0.092127) (15.2500,259.0000,0.092127)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,259.0000,0.016340) (17.6500,259.0000,0.016340) (17.6500,284.5000,0.016340) (15.2500,284.5000,0.016340)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(15.2500,284.5000,0.167400) (17.6500,284.5000,0.167400) (17.6500,455.0000,0.167400) (15.2500,455.0000,0.167400)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,68.0000,0.000000) (20.9000,68.0000,0.000000) (20.9000,70.5000,0.000000) (17.6500,70.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,70.5000,0.033445) (20.9000,70.5000,0.033445) (20.9000,93.5000,0.033445) (17.6500,93.5000,0.033445)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,93.5000,0.168734) (20.9000,93.5000,0.168734) (20.9000,109.0000,0.168734) (17.6500,109.0000,0.168734)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,109.0000,0.240670) (20.9000,109.0000,0.240670) (20.9000,159.5000,0.240670) (17.6500,159.5000,0.240670)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,159.5000,0.252029) (20.9000,159.5000,0.252029) (20.9000,259.0000,0.252029) (17.6500,259.0000,0.252029)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,259.0000,0.072398) (20.9000,259.0000,0.072398) (20.9000,284.5000,0.072398) (17.6500,284.5000,0.072398)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.6500,284.5000,0.054139) (20.9000,284.5000,0.054139) (20.9000,455.0000,0.054139) (17.6500,455.0000,0.054139)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,68.0000,0.168421) (25.6500,68.0000,0.168421) (25.6500,70.5000,0.168421) (20.9000,70.5000,0.168421)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,70.5000,0.077803) (25.6500,70.5000,0.077803) (25.6500,93.5000,0.077803) (20.9000,93.5000,0.077803)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,93.5000,0.407470) (25.6500,93.5000,0.407470) (25.6500,109.0000,0.407470) (20.9000,109.0000,0.407470)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,109.0000,0.385618) (25.6500,109.0000,0.385618) (25.6500,159.5000,0.385618) (20.9000,159.5000,0.385618)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,159.5000,0.086750) (25.6500,159.5000,0.086750) (25.6500,259.0000,0.086750) (20.9000,259.0000,0.086750)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,259.0000,0.020640) (25.6500,259.0000,0.020640) (25.6500,284.5000,0.020640) (20.9000,284.5000,0.020640)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(20.9000,284.5000,0.006791) (25.6500,284.5000,0.006791) (25.6500,455.0000,0.006791) (20.9000,455.0000,0.006791)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,68.0000,0.369231) (28.9000,68.0000,0.369231) (28.9000,70.5000,0.369231) (25.6500,70.5000,0.369231)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,70.5000,0.193980) (28.9000,70.5000,0.193980) (28.9000,93.5000,0.193980) (25.6500,93.5000,0.193980)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,93.5000,0.545906) (28.9000,93.5000,0.545906) (28.9000,109.0000,0.545906) (25.6500,109.0000,0.545906)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,109.0000,0.332064) (28.9000,109.0000,0.332064) (28.9000,159.5000,0.332064) (25.6500,159.5000,0.332064)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,159.5000,0.041747) (28.9000,159.5000,0.041747) (28.9000,259.0000,0.041747) (25.6500,259.0000,0.041747)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,259.0000,0.012066) (28.9000,259.0000,0.012066) (28.9000,284.5000,0.012066) (25.6500,284.5000,0.012066)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(25.6500,284.5000,0.008121) (28.9000,284.5000,0.008121) (28.9000,455.0000,0.008121) (25.6500,455.0000,0.008121)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,68.0000,0.124294) (46.6000,68.0000,0.124294) (46.6000,70.5000,0.124294) (28.9000,70.5000,0.124294)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,70.5000,0.262835) (46.6000,70.5000,0.262835) (46.6000,93.5000,0.262835) (28.9000,93.5000,0.262835)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,93.5000,0.302533) (46.6000,93.5000,0.302533) (46.6000,109.0000,0.302533) (28.9000,109.0000,0.302533)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,109.0000,0.054819) (46.6000,109.0000,0.054819) (46.6000,159.5000,0.054819) (28.9000,159.5000,0.054819)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,159.5000,0.007665) (46.6000,159.5000,0.007665) (46.6000,259.0000,0.007665) (28.9000,259.0000,0.007665)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,284.5000,0.000000) (28.9000,284.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(28.9000,284.5000,0.000166) (46.6000,284.5000,0.000166) (46.6000,455.0000,0.000166) (28.9000,455.0000,0.000166)};

			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {

### 2015-11-27 graph_auto_exp2_distr_1_3.tex
Modify based on Mykel's feedback

	\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=A,
			ylabel=C,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.0000) (17.5500,68.0000,0.0000) (17.5500,134.5000,0.0000) (9.0000,134.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.0010) (17.5500,134.5000,0.0010) (17.5500,159.5000,0.0010) (9.0000,159.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.0010) (17.5500,159.5000,0.0010) (17.5500,169.5000,0.0010) (9.0000,169.5000,0.0010)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.0395) (17.5500,169.5000,0.0395) (17.5500,259.0000,0.0395) (9.0000,259.0000,0.0395)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.0045) (17.5500,259.0000,0.0045) (17.5500,264.5000,0.0045) (9.0000,264.5000,0.0045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.2220) (17.5500,264.5000,0.2220) (17.5500,455.0000,0.2220) (9.0000,455.0000,0.2220)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.0765) (23.9500,68.0000,0.0765) (23.9500,134.5000,0.0765) (17.5500,134.5000,0.0765)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.0260) (23.9500,134.5000,0.0260) (23.9500,159.5000,0.0260) (17.5500,159.5000,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.0085) (23.9500,159.5000,0.0085) (23.9500,169.5000,0.0085) (17.5500,169.5000,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.1225) (23.9500,169.5000,0.1225) (23.9500,259.0000,0.1225) (17.5500,259.0000,0.1225)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.0070) (23.9500,259.0000,0.0070) (23.9500,264.5000,0.0070) (17.5500,264.5000,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.0355) (23.9500,264.5000,0.0355) (23.9500,455.0000,0.0355) (17.5500,455.0000,0.0355)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.3525) (46.6000,68.0000,0.3525) (46.6000,134.5000,0.3525) (23.9500,134.5000,0.3525)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.0770) (46.6000,134.5000,0.0770) (46.6000,159.5000,0.0770) (23.9500,159.5000,0.0770)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.0020) (46.6000,159.5000,0.0020) (46.6000,169.5000,0.0020) (23.9500,169.5000,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.0210) (46.6000,169.5000,0.0210) (46.6000,259.0000,0.0210) (23.9500,259.0000,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.0000) (46.6000,259.0000,0.0000) (46.6000,264.5000,0.0000) (23.9500,264.5000,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.0035) (46.6000,264.5000,0.0035) (46.6000,455.0000,0.0035) (23.9500,455.0000,0.0035)};

			\addplot3[mark=+, draw=none, mark size=0.7] coordinates {

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.24,...,1.3},
			        ylabel={probability density $\times 10^3$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,68.0000,0.000000) (17.5500,68.0000,0.000000) (17.5500,134.5000,0.000000) (9.0000,134.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,134.5000,0.004678) (17.5500,134.5000,0.004678) (17.5500,159.5000,0.004678) (9.0000,159.5000,0.004678)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,159.5000,0.011696) (17.5500,159.5000,0.011696) (17.5500,169.5000,0.011696) (9.0000,169.5000,0.011696)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,169.5000,0.051619) (17.5500,169.5000,0.051619) (17.5500,259.0000,0.051619) (9.0000,259.0000,0.051619)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,259.0000,0.095694) (17.5500,259.0000,0.095694) (17.5500,264.5000,0.095694) (9.0000,264.5000,0.095694)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(9.0000,264.5000,0.136299) (17.5500,264.5000,0.136299) (17.5500,455.0000,0.136299) (9.0000,455.0000,0.136299)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,68.0000,0.179746) (23.9500,68.0000,0.179746) (23.9500,134.5000,0.179746) (17.5500,134.5000,0.179746)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,134.5000,0.162500) (23.9500,134.5000,0.162500) (23.9500,159.5000,0.162500) (17.5500,159.5000,0.162500)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,159.5000,0.132813) (23.9500,159.5000,0.132813) (23.9500,169.5000,0.132813) (17.5500,169.5000,0.132813)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,169.5000,0.213862) (23.9500,169.5000,0.213862) (23.9500,259.0000,0.213862) (17.5500,259.0000,0.213862)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,259.0000,0.198864) (23.9500,259.0000,0.198864) (23.9500,264.5000,0.198864) (17.5500,264.5000,0.198864)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(17.5500,264.5000,0.029117) (23.9500,264.5000,0.029117) (23.9500,455.0000,0.029117) (17.5500,455.0000,0.029117)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,68.0000,0.234029) (46.6000,68.0000,0.234029) (46.6000,134.5000,0.234029) (23.9500,134.5000,0.234029)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,134.5000,0.135982) (46.6000,134.5000,0.135982) (46.6000,159.5000,0.135982) (23.9500,159.5000,0.135982)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,159.5000,0.008830) (46.6000,159.5000,0.008830) (46.6000,169.5000,0.008830) (23.9500,169.5000,0.008830)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,169.5000,0.010359) (46.6000,169.5000,0.010359) (46.6000,259.0000,0.010359) (23.9500,259.0000,0.010359)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,259.0000,0.000000) (46.6000,259.0000,0.000000) (46.6000,264.5000,0.000000) (23.9500,264.5000,0.000000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(23.9500,264.5000,0.000811) (46.6000,264.5000,0.000811) (46.6000,455.0000,0.000811) (23.9500,455.0000,0.000811)};

			\addplot3[mark=+, draw=none, mark size=1.0, jitter = 0.1] coordinates {

### 2015-11-27 graph_housing_exp1_distr_8_5.tex
Modify based on Mykel's feedback

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=H,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=1.0,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=1.0,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-11-27 graph_housing_exp2_distr_3_5.tex
Modify based on Mykel's feedback

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=C,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=1,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$C$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=1,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-11-27 graph_housing_exp2_distr_8_5.tex
Modify based on Mykel's feedback

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=H,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=0.4,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.08,...,0.41},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.4,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.08,...,0.41},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]
